---
title: "Activity: Street or Road?"
author: "Daniel Gao"
output: html_notebook
---

## Load in the data

```{r}
#load libraries 
library(tidyverse)
#load in the data here 
# we will only be using the "street-addresses.csv" file from the text
Addresses <- read_csv("https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv")

```

## Recreate Solved Example using `sample(50)`

```{r}
Sample <- Addresses %>%
  sample(size = 50, replace = T)

```

## Recreate Soved Example using the entire `Address` data set

```{r}
Matches <- 
  Addresses %>%
  filter(grepl(pattern = "PO", address))

```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}
Addresses %>%
  filter(grepl(pattern = "(PO BOX |NSCU BOX)", address)) %>%
  summarise(addresses = n())
s```

My answer here...... 

There are a total of 8249 address with PO BOX or NCSU BOX


## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl(" BOX ", address)
          )
```

My answer here.......
Line 1: Assign "(ST|RD|ROAD)" to the pattern

Line 2: Assign Leftover with results from the code below

Line 3: Addresses data is accessed through a pipe

Line 4: filters out adresses that does not contain ST or RD or ROAD  in the variable address. The grepl
fucntion allows for pattern matching.

Line 5: filters out adresses that does not contain APT or UNIT along any white spaces AND any digits. The grepl allows for pattern matching.

Line 6: filters out any address with does not contains " BOX " exactly.The grepl allows for pattern matching.


#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}
patterns <- "(NSCU)"
Test <-
  Addresses %>% 
  filter(grepl(pattern, address),
         !grepl("RD|ROAD", address))
         pattern <- "(ST|RD|ROAD)"
         

pattern <- "(ST|RD|ROAD|DR|CT|LN|NSCU|APT|DRIVE)"
New <-
  Addresses %>% 
  filter(grepl(pattern, address)) %>%
   tidyr::extract(col = address, into = "Street", regex = pattern)
```

My answer here.......
Line 1: "(ST|RD|ROAD|DR|CT|LN|NSCU|APT)" is assigned to patterns

Line 2: New is assigned to the result of the code below

Line 3: Addresses data is access through a pipe

Line 4: filters out the addresses that contains ST or RD or ROAD or DR or CT or LN or NSCU or DRIVE. The grepl allows for pattern matching.

Line 5: tidyr::extract() was used to extract only the names from pattern. 

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}
New %>% 
  group_by(Street) %>%
  summarise(popularity = n()) %>%
  arrange(desc(popularity)) %>%
  head(10) %>%
  ggplot(aes(x = reorder(Street, -popularity), y = popularity)) +
  geom_point(shape = "circle", size = 1) +
  xlab("street name")

```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}
New %>% 
  group_by(Street) %>%
  summarise(popularity = n()) %>%
  arrange(desc(popularity)) %>%
  head(10) %>%
  ggplot(aes(x = reorder(Street, -popularity), y = popularity)) +
  geom_col(fill = "blue") +
  xlab("street name")
```

#### Additional Question 3: Comment on any patterns you see

My answer here.......
Within 8 street names, ST was the most common, DR the second most common, and RD the third most common. NSCU is the least common street name.  
